---
title: " Data Scienctist Skills: Compared"
author: "Joseph Simone & Kigamba Samuel"
date: "10/22/2019"
output: ioslides_presentation
---

```{r setup, include=FALSE}
library(XML)
library(RCurl)
library(knitr)
library(dplyr)
library(plyr)
library(tidyr)
library(plotly)
library(tidyselect)
library(tidyverse)
library(data.table)
library(png)

```

##  Background 

- During early research, 

- We found this study 

- https://365datascience.com/research-into-1001-data-scientist-profiles/ 

```{r, include=TRUE }
imgage <- "C:/Users/jpsim/Documents/DATA Acquisition and Management/journal.png"
include_graphics(imgage)
```

***

- As a team we saw similiar findings that fits the critia needed to be calculated in    order to complete this project. 

- However, as a team, we needed some sort of data pool to start calulating perameters   to answer a research question(s).


- With some futher research, we found a similar project that wanted to answer a          similar   question. 


-https://www.kaggle.com/discdiver/the-most-in-demand-skills-for-data-scientists

***

```{r, include=TRUE }
imgage <- "C:/Users/jpsim/Documents/DATA Acquisition and Management/kaggle.png"
include_graphics(imgage)
```

***

- We decided to use the two main data sets from this kaggle project as our data pool    to try and make futher analysis

```{r, include=TRUE }
imgage <- "C:/Users/jpsim/Documents/DATA Acquisition and Management/kaggle_data.png"
include_graphics(imgage)
```


***

```{r}
 general_skills <- read_csv(file="https://raw.githubusercontent.com/josephsimone/DATA_607_Project_3/master/kaggle_ds_general_skills_revised.csv")
head(general_skills)
```

***

```{r}
software_skills <-read_csv(file = "https://raw.githubusercontent.com/josephsimone/DATA_607_Project_3/master/kaggle_ds_job_listing_software.csv")
head(software_skills)
```

## Research Question(s)


- What are the most important Techology based skill and Soft Skill, respectively, when   hiring a Data Scientist?



- Overall, what is the most sought after skill for a Data Scientist? 

## Data import and cleaning

- As a team, we thought it be best to join these two data-sets, cleaning the             respective data-frames into similar formats to be merged. 
 
```{r}
dt1 <- as_tibble(general_skills, key = "ï..Keyword")
dt1$Skill_Set <- "Soft"
dt2 <- as_tibble(software_skills, key = "ï..Keyword")
dt2$Skill_Set <- "Tech"
dt2 <- select(dt2,-c(6,7,8,9,10,11,12))
```


## Combine Data-frames

```{r}
result<-rbind(dt1, dt2)
names(result)[names(result) == "ï..Keyword"] <- "Keyword"
head(result)
```

## Data-frame cleaning and tidying

```{r}
ds_skills <- as.data.frame(result)
ds_skills$Total <- rowSums(sapply(ds_skills[,c(2:5)], as.numeric))
ds_skills <- mutate(ds_skills[, c(1,6,2:5,7)])
ds_skills <- data.frame(ds_skills)
colnames(ds_skills)
head(ds_skills)
```

## Creation of New Variable 

These two combined data-sets used the amount of keywords present during a general search on well known job recruitment websites, to fill in its' values. As a team, we thought it was more effective to create an average out of these values to get a better understanding of the dataset.

***
```{r, message=FALSE, warning= FALSE}
LinkedIn <- 8610
Indeed <- 5138
SimplyHired <- 3829
Monster <- 3746
Total <- LinkedIn + Indeed + SimplyHired + Monster
ds_skills$LinkedIn <- ((ds_skills$LinkedIn)/(LinkedIn*100))
ds_skills$Indeed <- ((ds_skills$Indeed)/(Indeed*100))
ds_skills$SimplyHired <- ((ds_skills$SimplyHired)/(SimplyHired*100))
ds_skills$Monster <- ((ds_skills$Monster)/((Monster*10)))
ds_skills$Total <- ((ds_skills$Total/((Total*100))))
```




***

Set up for Bar Graphs

```{r}
ds_skills_soft <- filter(ds_skills, ds_skills$Skill_Set == "Soft")
dim(ds_skills_soft)
head(ds_skills_soft, 20)
ds_skills_soft <- arrange(ds_skills_soft, desc(Total))

top_10_soft <- ds_skills_soft[1:10,c(1,3:7)]
top_10_soft
```

 
***
 Top Ten Non-Technical skills as a percentage of total Data Science jobs

```{r, include=FALSE}
p <- plot_ly(ds_skills_soft, x = ~ ds_skills_soft, y = ds_skills_soft$Total, type = 'bar', name = ds_skills_soft$Keyword)

```


```{r}
p
```


***

 Top 5 Technical Skills for Data Scientists

Data transformations for visualization




***
```{r}

ds_skills_tech <- filter(ds_skills, ds_skills$Skill_Set == "Tech")

#Arrange data from largest to smallest by the Totals column
ds_skills_tech <- arrange(ds_skills_tech, desc(Total))

#Filter out only the Top 10 technical skills
top_10_tech <- ds_skills_tech[1:10,c(1,3:7)]

```


***
 Top Ten Technical skills as a percentage of total Data Science jobs

```{r, include=FALSE}
x <- plot_ly(top_10_tech, x = ~ top_10_tech, y = top_10_tech$Total, type = 'bar', name = top_10_tech$Keyword)
```


```{r}
x
```



***
Top 10 Tech Skills as an average pecentage of total data science jobs by job site

```{r, eval=TRUE, message = FALSE, warning=FALSE}
top_10_tech_visual <- data.frame("Keyword"=top_10_tech, top_10_tech)

data <- top_10_tech_visual[,c('Keyword', 'LinkedIn', 'Indeed', 'SimplyHired', 'Monster', 'Total')]
```

***

```{r, eval=TRUE, message = FALSE, warning=FALSE, include=FALSE}
s <- plot_ly(data, x = ~Keyword, y = ~LinkedIn, type = 'bar', name = "Linkedin") %>%
add_trace(y = ~Indeed, name = "Indeed") %>% 
add_trace(y = ~SimplyHired, name = "SimplyHired") %>% 
add_trace(y = ~Monster, name = "Monster") %>% 
add_trace(y = ~Total, name = "Average") %>% 
layout(title = 'Technical Skills by Job Sites', yaxis = list(title = '% of Data Science Jobs'), xaxis = list(title = 'Tech Skills'), barmode = 'group')
```


```{r, eval=TRUE, message = FALSE, warning=FALSE}
s
```

***

 Top 10 Non-Tech SKills as an average pecentage of total data science jobs by job site

```{r, eval=TRUE, message=FALSE, warning=FALSE}
top_10_soft_visual <- data.frame("Keyword"=top_10_soft, top_10_soft)

```

***
```{r, eval=TRUE, message=FALSE, warning=FALSE}
data2 <- top_10_soft_visual[,c('Keyword', 'LinkedIn', 'Indeed', 'SimplyHired', 'Monster', 'Total')]

```
***

```{r, eval=TRUE, message=FALSE, warning=FALSE, include=FALSE}
t <- plot_ly(data2, x = ~Keyword, y = ~LinkedIn, type = 'bar', name = "Linkedin") %>%
add_trace(y = ~Indeed, name = "Indeed") %>% 
add_trace(y = ~SimplyHired, name = "SimplyHired") %>% 
add_trace(y = ~Monster, name = "Monster") %>% 
add_trace(y = ~Total, name = "Average") %>% 
layout(title = 'Non-Technical Skills by Job Sites', yaxis = list(title = '% of Data Science Jobs'), xaxis = list(title = 'Non-Tech Skills'), barmode = 'group')
```


```{r, eval=TRUE, message=FALSE, warning=FALSE}
t
```


## Top two "Technology" Skills for Data Scientist 
```{r}
head(ds_skills_tech, 2)
```

## Top two "Non-Technology" Skills for Data Scientist 
```{r}
head(ds_skills_soft, 2)
```

## Conclusion 

There are many skills and skill-sets that employers are looking for when hiring a data-scientist. Given that Data Science is amultidisciplinary field, it is only fitting that there are both Techology based skills and Soft skills that companies look for in a data science. 

The top Techology skill that employers are looking for when hiring a data scientist, according to this dataset, is Python. 

The top Soft skill that employers are looking for when hiring a data scientist, according to this dataset, is Analysis.

The top Overall skill that employers are looking for when hiring a data scientist, according to this dataset, is Analysis.
