---
title: "Data_603_Project_3_Clean"
author: "Joseph Simone & Kigamba Samuel"
date: "10/18/2019"
output: html_document
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
 library(XML)
library(RCurl)
library(knitr)
library(dplyr)
library(plyr)
library(tidyr)
library(tidyverse)
library(tidyselect)
library(data.table)
```

```{r}
 general_skills <- read.csv(file="https://raw.githubusercontent.com/josephsimone/DATA_607_Project_3/master/kaggle_ds_general_skills_revised.csv")
head(general_skills)
```

```{r}
software_skills <-read.csv(file = "https://raw.githubusercontent.com/josephsimone/DATA_607_Project_3/master/kaggle_ds_job_listing_software.csv")
```




```{r}
 dt1 <- data.table(general_skills, key = "ï..Keyword")
dt1$Skill_Set <- "Soft"
dt2 <- data.table(software_skills, key = "ï..Keyword")
dt2$Skill_Set <- "Tech"
 dt2 = subset(dt2, select = -c(LinkedIn.., Indeed.., SimplyHired.., Monster.., Avg.., GlassDoor.Self.Reported...2017, Difference) )
 
result<-rbind(dt1, dt2)
```



```{r}
head(result)
```

```{r}
names(result)[names(result) == "ï..Keyword"] <- "Keyword"
```


```{r}
write.csv(result, file = "joined_df2.csv",row.names=FALSE)
```

```{r}
ds_skills <- read.csv("joined_df2.csv")
head(ds_skills)
ds_skills$Total <- rowSums(sapply(ds_skills[,c(2:5)], as.numeric))
ds_skills <- mutate(ds_skills[, c(1,6,2:5,7)])
ds_skills <- data.frame(ds_skills)
colnames(ds_skills)
head(ds_skills)
LinkedIn <- 8610
Indeed <- 5138
SimplyHired <- 3829
Monster <- 3746
Total <- LinkedIn + Indeed + SimplyHired + Monster
ds_skills$LinkedIn <- ((ds_skills$LinkedIn)/(LinkedIn*100))
ds_skills$Indeed <- ((ds_skills$Indeed)/(Indeed*100))
ds_skills$SimplyHired <- ((ds_skills$SimplyHired)/(SimplyHired*100))
ds_skills$Monster <- ((ds_skills$Monster)/((Monster*10)))
ds_skills$Total <- ((ds_skills$Total/((Total*100))))
head(ds_skills)
```
# Top 10 Soft Skills for Data Scientists

### Data transformations for visualization

```{r}
ds_skills_soft <- filter(ds_skills, ds_skills$Skill_Set == "Soft")
dim(ds_skills_soft)
head(ds_skills_soft, 20)
ds_skills_soft <- arrange(ds_skills_soft, desc(Total))
head(ds_skills_soft, 2)
#Top 10 soft skills
ds_skills_soft <- ds_skills_soft[1:10,c(1,3:7)]
head(ds_skills_soft, 2)
#ds_skills_soft$Keyword
```


# Top ten Soft skills as a percentage of total Data Science jobs

```{r}
p <- plot_ly(ds_skills_soft, x = ~ ds_skills_soft, y = ds_skills_soft$Total, type = 'bar', name = ds_skills_soft$Keyword)
p
```


#Bar Graphs
## Top 10 Soft as a pecentage of total data science jobs by job site

```{r}
top_10_soft_visual <- data.frame("Keyword"=ds_skills_soft, ds_skills_soft)
head(top_10_soft_visual, 2)
data_soft <- top_10_soft_visual[,c('Keyword', 'LinkedIn', 'Indeed', 'SimplyHired', 'Monster', 'Total')]
head(data_soft, 2)
q <- plot_ly(data_soft, x = ~Keyword, y = ~LinkedIn, type = 'bar', name = "Linkedin") %>%
  add_trace(y = ~Indeed, name = "Indeed") %>% 
  add_trace(y = ~SimplyHired, name = "SimplyHired") %>% 
  add_trace(y = ~Monster, name = "Monster") %>% 
  add_trace(y = ~Total, name = "Average") %>% 
  layout(title = 'Soft Skills by Job Site', yaxis = list(title = '% of Data Science Jobs'), xaxis = list(title = 'Soft Skills'), barmode = 'group')
q
```


# Top 10 Non-Technical Skills for Data Scientists

### Data transformations for visualization

```{r}
ds_skills_soft <- filter(ds_skills, ds_skills$Skill_Set == "Soft")
dim(ds_skills_soft)
# View first 20 non-technical skills
head(ds_skills_soft, 20)
#Arrange data from largest to smallest by the Totals column
ds_skills_tech <- arrange(ds_skills_soft, desc(Total))
head(ds_skills_soft, 2)
#Filter out only the Top 10 non-technical skills
top_10_soft <- ds_skills_soft[1:10,c(1,3:7)]
head(top_10_soft, 2)

```


# Top 10 Technical Skills for Data Scientists

### Data transformations for visualization

```{r}
ds_skills_tech <- filter(ds_skills, ds_skills$Skill_Set == "Tech")
dim(ds_skills_tech)
# View first 20 skills
head(ds_skills_tech, 20)
#Arrange data from largest to smallest by the Totals column
ds_skills_tech <- arrange(ds_skills_tech, desc(Total))
head(ds_skills_tech, 2)
#Filter out only the Top 10 technical skills
top_10_tech <- ds_skills_tech[1:10,c(1,3:7)]
head(top_10_tech, 2)
#top_10_tech$Keyword
```


### Top ten Technical skills as a percentage of total Data Science jobs

```{r}
x <- plot_ly(top_10_tech, x = ~ top_10_tech, y = top_10_tech$Total, type = 'bar', name = top_10_tech$Keyword)
x
```


### Top ten Technical skills as a percentage of total Data Science jobs

```{r}
y <- plot_ly(top_10_soft, x = ~ top_10_soft, y = top_10_soft$Total, type = 'bar', name = top_10_soft$Keyword)
y
```



##Bar Graphs
### Top 10 Techs as a pecentage of total data science jobs by job site

```{r, eval=TRUE}
top_10_tech_visual <- data.frame("Keyword"=top_10_tech, top_10_tech)
head(top_10_tech_visual, 2)
data <- top_10_tech_visual[,c('Keyword', 'LinkedIn', 'Indeed', 'SimplyHired', 'Monster', 'Total')]
head(data, 2)
s <- plot_ly(data, x = ~Keyword, y = ~LinkedIn, type = 'bar', name = "Linkedin") %>%
  add_trace(y = ~Indeed, name = "Indeed") %>% 
  add_trace(y = ~SimplyHired, name = "SimplyHired") %>% 
  add_trace(y = ~Monster, name = "Monster") %>% 
  add_trace(y = ~Total, name = "Average") %>% 
  layout(title = 'Technical Skills by Job Sites', yaxis = list(title = '% of Data Science Jobs'), xaxis = list(title = 'Tech Skills'), barmode = 'group')
s
```



##Bar Graphs
### Top 10 Techs as a pecentage of total data science jobs by job site

```{r, eval=TRUE}
top_10_soft_visual <- data.frame("Keyword"=top_10_soft, top_10_soft)
head(top_10_soft_visual, 2)
data2 <- top_10_soft_visual[,c('Keyword', 'LinkedIn', 'Indeed', 'SimplyHired', 'Monster', 'Total')]
head(data, 2)
t <- plot_ly(data2, x = ~Keyword, y = ~LinkedIn, type = 'bar', name = "Linkedin") %>%
  add_trace(y = ~Indeed, name = "Indeed") %>% 
  add_trace(y = ~SimplyHired, name = "SimplyHired") %>% 
  add_trace(y = ~Monster, name = "Monster") %>% 
  add_trace(y = ~Total, name = "Average") %>% 
  layout(title = 'Non-Technical Skills by Job Sites', yaxis = list(title = '% of Data Science Jobs'), xaxis = list(title = 'Non-Tech Skills'), barmode = 'group')
t
```



